# scaler

<!-- badges: start -->
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check.yaml](https://github.com/danielvartan/scaler/actions/workflows/check-standard.yaml/badge.svg)](https://github.com/danielvartan/scaler/actions/workflows/check-standard.yaml)
[![Codecov test coverage](https://codecov.io/gh/danielvartan/scaler/branch/main/graph/badge.svg)](https://app.codecov.io/gh/danielvartan/scaler?branch=main)
[![License: MIT](https://img.shields.io/badge/license-MIT-green)](https://choosealicense.com/licenses/mit/)
[![Contributor Covenant](https://img.shields.io/badge/Contributor%20Covenant-2.1-4baaaa.svg)](CODE_OF_CONDUCT.md)
<!-- badges: end -->

## Overview

`scaler` is an R package that provides a set of tools to deal with health measurement scales. Its aim is to facilitate the work of researchers with these kind of data and to improve reproducibility in research.

Some scales require a dedicated package. If you're looking for tools to process the Munich ChronoType Questionnaire ([MCTQ](https://doi.org/10.1177/0748730402239679)), please check the [`mctq`](https://github.com/ropensci/mctq) package.

## Installation

You can install `scaler` using the [`remotes`](https://github.com/r-lib/remotes) package:

``` {r}
#| eval: false

remotes::install_github("danielvartan/scaler")
```

## Citation

If you use `scaler` in your research, please consider citing it. We put a lot of work to build and maintain a free and open-source R package. You can find the citation below.

```{r}
citation("scaler")
```

## Contributing

We welcome contributions, including bug reports. Take a moment to review our [Guidelines for Contributing](https://danielvartan.github.io/scaler/CONTRIBUTING.html).

## License

[![License:
MIT](https://img.shields.io/badge/license-MIT-green)](https://opensource.org/license/mit/)

`scaler` code is released under the [MIT license](https://opensource.org/license/mit/).

<br>

Become an `scaler` supporter!

Click [here](https://github.com/sponsors/danielvartan) to make a donation. Please indicate the `scaler` package in your donation message.
