---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(scaler)
```

# scaler

<!-- badges: start -->
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/giperbio/scaler/workflows/R-CMD-check/badge.svg)](https://github.com/giperbio/scaler/actions)
[![Codecov test coverage](https://codecov.io/gh/giperbio/scaler/branch/main/graph/badge.svg)](https://codecov.io/gh/giperbio/scaler?branch=main)
[![License: MIT](https://img.shields.io/badge/license-MIT-green)](https://choosealicense.com/licenses/mit/)
[![Contributor Covenant](https://img.shields.io/badge/Contributor%20Covenant-v2.0%20adopted-ff69b4.svg)](https://giperbio.github.io/scaler/CODE_OF_CONDUCT.html)
<!-- badges: end -->

## Overview

`scaler` is an R package that provides a set of tools to deal with health measurement scales. Its aim is to facilitate the work of researchers with these kind of data and to improve reproducibility in research.

Some scales require a dedicated package. If you're looking for tools to process the Munich ChronoType Questionnaire ([MCTQ](https://doi.org/10.1177/0748730402239679)), please check the [`mctq`](https://github.com/ropensci/mctq) package.

## Prerequisites

You need to have some familiarity with the [R programming language](https://www.r-project.org/) to use `scaler` main functions.

If you don't feel comfortable with R, we strongly recommend checking Hadley Wickham and Garrett Grolemund's free and online book [R for Data Science](https://r4ds.had.co.nz/) and the Coursera course from John Hopkins University [Data Science: Foundations using R](https://www.coursera.org/specializations/data-science-foundations-r) (free for audit students).

## Installation

You can install `scaler` with:

``` {r, eval = FALSE}
# install.packages("remotes")
remotes::install_github("giperbio/scaler")
```

## Citation

If you use `scaler` in your research, please consider citing it. We put a lot of work to build and maintain a free and open-source R package. You can find the `scaler` citation below.

```{r}
citation("scaler")
```

## Contributing

We welcome contributions, including bug reports.

Take a moment to review our [Guidelines for Contributing](https://giperbio.github.io/scaler/CONTRIBUTING.html).

<br>

Become an `scaler` supporter!

Click [here](https://github.com/sponsors/danielvartan) to make a donation. Please indicate the `scaler` package in your donation message.
